\begin{center}
	{\huge{\textbf{Acknowledgements}}}
\end{center}

I would like to express my sincere gratitude towards my thesis supervisor Prof. Anil Seth for his constant support and encouragement. He gave me complete freedom to work according to my interests and comfort. The meetings and discussions that I had with him gave a proper direction to my efforts.

I would also like to thank the faculty and staff of the Department of CSE for the beautiful academic environment that they have created here. I also thank the administrative staff of IIT Kanpur for the constant efforts they put to make everything run smoothly.

I am thankful to all my friends here at IIT Kanpur. I got to learn a lot with them and I got the company of some really nice people who made these two years memorable for me. In particular, I would like to thank Akhil, Ajay, Ankit, Ashu, Atanu, Hrishit, Manash, Mangat, Nitesh, Parveen, Prashant, Shahbaz, Sourabh and Vinay for all the learning and fun we had together. I would also like to thank Tejas for really looking after the Y11 batch like an elder brother. He has been a great friend and a great guide, someone we all look up to.

I thank the office staff and workers in my hostel, especially, the mess workers, the canteen workers, gardeners, sweepers and washer-men. These people have had a very important role in making my stay at IIT Kanpur really comfortable.

I would like to thank my cousin Dr. Parvez Memon and his family who live in Kanpur. I frequently visited them during my stay here and got a homely environment.

I am thankful to my best friends Nupoor, Shubham and Tanya, who for the last five years, have always been there for me.

Last, but not the least, I would like to thank my parents and my brother for their love, constant support and encouragement. Without their support and patience this work would not have been possible.

\vskip 4mm
\begin{flushright}
\textit{\textbf{Mohammed Rizwan Rawani}}
\end{flushright}
